Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2018-01-19 ms.tex
fixes

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/twopanel_dayside_spectrum.pdf}
\caption{Dayside planet-to-star flux (points) compared to a blackbody model (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right). The 1D model was fit to all the data simultaneously, but the blackbody was fit to the WFC3 data only. The best fit 1D model binned at the resolution of the \Spitzer\ data is indicated by blue squares (right). } 
\label{fig:dayside}
\end{figure*}

@@

\acknowledgments
Support for \textit{HST} program GO-15050 was provided by NASA through a grant from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555. Support for \textit{Spitzer} program 11099 was provided by NASA through an award issued by JPL/Caltech.  The data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared Science Archive. STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. The Infrared Science Archive is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.  This work also made use of the Python packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}. The authors are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg Atmospheres of Disks and Planets meeting for facilitating productive discussion and collaboration.
J.L.B. acknowledges support from the David and Lucile Packard Foundation.

>>>>

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/twopanel_dayside_spectrum.pdf}
\caption{Dayside planet-to-star flux (points) compared to a blackbody model for the planet (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right). The 1D model was fit to all the data simultaneously, but the blackbody was fit to the WFC3 data only. The best fit 1D model binned at the resolution of the \Spitzer\ data is indicated by blue squares (right).} 
\label{fig:dayside}
\end{figure*}

@@

\acknowledgments
Support for \textit{HST} program GO-15050 was provided by NASA through a grant from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555. Support for \textit{Spitzer} program 11099 was provided by NASA through an award issued by JPL/Caltech.  The data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared Science Archive. STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. The Infrared Science Archive is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.  This work also made use of the Python packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}. The authors are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg Atmospheres of Disks and Planets meeting for facilitating productive discussion and collaboration.  J.L.B. acknowledges support from the David and Lucile Packard Foundation.  J.M.D. acknowledges support from the European Research Council (ERC) under the programme Exo-Atmos (grant agreement no. 679633).
